---
title: "Data Selection Description"
author: "Joshua Ferris"
date: "8/21/2020"
output:
  pdf_document: default
  html_document:
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
setwd('/Users/joshua/Downloads/BeachTan')
df = read.csv('BeachTan.csv', stringsAsFactors = TRUE)
```
  
## The number of observations

```{r}
nrow(df)
```

The Beach Tan data set has $11,041$ observations.

## The number of variables

```{r}
ncol(df)
```

The Beach Tan data set has $12$ variables.

## The data type of each variable

Some of the variables were typed incorrectly and so I will convert them to factors.

```{r}
df$UIDStoreLocation = factor(df$UIDStoreLocation)
df$MembershipType = factor(df$MembershipType)
df$MembershipLevel = factor(df$MembershipLevel)
str(df)
```

* Factor: UIDStoreLocation, Gender, DateJoined, MembershipType, and MembershipLevel.
* Int: UIDClient, DaysSinceJoined, Age, UVTans, SunlessTans, and UpgradeRevenue.
* Num: RetailRevenue.

## The levels of each factor

```{r}
levels(df$UIDStoreLocation)
levels(df$Gender)
head(levels(df$DateJoined))
levels(df$MembershipType)
levels(df$MembershipLevel)
```

* UIDStoreLocation: 1, 2, 3, 4, 5, 6, 7, 8, 9, and 10.
* Gender: "", "#NULL!", "0", and "1".
* DateJoined: "", "1/1/2008", 1/1/2011", "1/10/2002", "1/10/2003", "1/10/2004", and many more dates.
* MembershipType: 0, 1, and 2.
* MembershipLevel: 0, 1, 2, 3, and 4.

## The amount of missingness in the data (DataExplorer)

```{r}
library(DataExplorer)
profile_missing(df)
```

The above output tells us that the data set has no missing data. However, from looking at the data manually, I have observed empty characters and "#NULL!" in the Gender column. In the date column there are some empty character string also. We will want to clean these values before we perform any analysis.

## High-level overview of the analysis I will conduct

I theorize that the more active a client is in their tanning services, the more retail revenue they will generate. To test this theory I will perform some explanatory analysis on the data using linear regression on the response variable RetailRevenue.
